SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-13 paper/abstract.tex
cnf
back-abstract

In Biology, there are several questions that translate to combinatorial 
search.
%
For example, vesicle traffic systems in biological cells exhibit
several graph properties such as three connectivity and
a natural question arises for biologists that what are all possible
networks for various combinations of those properties.
%
It will help biologists for .....
%
In this paper, we present SAT/QBF encodings of the properties over
vesicle traffic systems and a tool that searches for the networks
that satisfies the properties using SAT/QBF solvers.
%
In our experiments, we show that our tool can search for networks of
sizes that are considered to be relevant by biologists.

>>>>

In biology, there are several questions that translate to combinatorial
search. For example, vesicle traffic systems that move cargo within
eukaryotic cells have been proposed to exhibit several graph properties
such as three connectivity. These properties are consequences of underlying
biophysical constraints. A natural question for biologists is: what are all
possible networks for various combinations of those properties? In this
paper, we present SAT/QBF encodings of the properties over vesicle traffic
systems and a tool that searches for the networks that satisfies the
properties using SAT/QBF solvers. In our experiments, we show that our tool
can search for networks of sizes that are considered to be relevant by
biologists.
